Precision calculations of the cosmic shear power spectrum projection

### 2017-02-20 limber2.tex
Added funding (PS)

The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk,
Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful
discussions. This work was financially supported by the DFG (Emmy Noether grant
Hi 1495/2-1; SI 1769/1-1; TR33 `The Dark Universe'), the Alexander von Humboldt
Foundation, the ERC (grants 279396, 647112), the Seventh Framework Programme of
the European Commission (Marie Sklodwoska Curie Fellowship grant 656869), the
Netherlands Organisation for Scientific Research (NWO) (grants 614.001.103),
NSERC, CIfAR, and the World Premier International Research Center Initiative
(WPI), MEXT, Japan. Parts of this research were conducted by the Australian
Research Council Centre of Excellence for All-sky Astrophysics (CAASTRO),
through project number CE110001020.

>>>>

The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk,
Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful
discussions. This work was financially supported by the DFG (Emmy Noether grant
Hi 1495/2-1; SI 1769/1-1; TR33 `The Dark Universe'), the Alexander von Humboldt
Foundation, the ERC (grants 279396, 647112), the Seventh Framework Programme of
the European Commission (Marie Sklodwoska Curie Fellowship grant 656869), the
Netherlands Organisation for Scientific Research (NWO) (grants 614.001.103),
NSERC, CIfAR, and the World Premier International Research Center Initiative
(WPI), MEXT, Japan. Parts of this research were conducted by the Australian
Research Council Centre of Excellence for All-sky Astrophysics (CAASTRO),
through project number CE110001020i, and by the German Federal
Ministry for Economic Affairs and Energy (BMWi) under
project no. 50QE1103.
